\textbf{Causal graph quantum dynamic simulation}

### 2021-06-02 paper/paper.tex
optimized the reduce step

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

>>>>

\begin{lstlisting}[style=CStyle]
	//...
	void reduce_all() {
		for(auto it = graphs_.begin(); it != graphs_.end();) {
    	// range of similar graphs to delete
    	auto range = graphs_.equal_range(it->first);
    	auto start = range.first;

    	for(auto jt = std::next(it); jt != range.second; ++jt)
        	it->second += jt->second;

    	// if the first graphgs has a zero probability, erase the whole range
    	if (!check_zero(it->second))
    		++start;

    	it = graphs_.unsafe_erase(start, range.second);
	}
	//...
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
	//...
	void step_split_merge_all(bool step, bool split_merge, bool reversed) {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
	  	for (auto & [graph, mag] : buff)
		#pragma omp task
	  	{
	  		if (step)
	  			graph->step();

	  		if (reversed)
	  			graph->reversed_step();

	  		if (split_merge) {
	  			auto split_merge = get_split_merge(graph);

				// add all graphs that actually have some split ot merge 
				const int n_max = num_subset(split_merge);
				#pragma omp taskloop
				for (int j = 1; j < n_max; ++j) {
					graph_t* g_ = graph->copy();

					auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);
				  	g_->split_merge(split_merge_list);

				  	//add graph
				  	graphs_.insert({g_, mag * mag_split_merge});
				}
				// update the probability of the graph without split or merge 
				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);
				mag *= mag_no_split_merge;
	  		}

	  		//add graph
			graphs_.insert({graph, mag});
	  	}
	}
	//...
\end{lstlisting}
